EDA

### 2020-02-28 src/draft.Rmd
model added

>>>>

3. Fit linear model
```{r}

linear1<-lm(rate_pct~factor(Year)+factor(TaxClassCode)+factor(Municipalities)+assessTotal_pct+tax,data=pct_final)
summary(linear1)

linear2<-lm(rate_pct~factor(TaxClassCode)+factor(Municipalities)+assessTotal_pct+tax,data=pct_final)
summary(linear2)
library(glmnet)

x_matrix<-pct_final[,-c(8)]
x_matrix[,1]<-factor(x_matrix$Year)
x_matrix[,2]<-factor(x_matrix$Municipalities)
x_matrix[,3]<-factor(x_matrix$TaxClassCode)
x_matrix<-x_matrix[,-c(5,6,7)]
x_matrix<-as.matrix(x_matrix)

lambdas <- 10^seq(2, -3, by = -.1)
ridge_reg = glmnet(x_matrix, pct_final$rate_pct, nlambda = 25, alpha = 0, family = 'gaussian', lambda = lambdas)

summary(ridge_reg)
